\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-21 tex/paper.tex
Added branching section

>>>>

\subsection{Branching}
Branching was also implemented in Perius, but to not make the report too wide it was not included.
The branching worked by the user selecting a container that the branch should be based on and a
container in which the branch should be places. The user could then choose which containers and
content that it wanted to update with the origin source of and which objects that should be deep
copied to the new branch.
